
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Développement d’agents d’IA pour l’automatisation de cas d’utilisation concrets en entreprise}

\author{Mohamed Iheb Ben Cheikh Larbi}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{Diplôme National d'Ingénieur en Sciences Appliquées et Technologiques}
\speciality{Génie Logiciel et Systèmes d’Information}
%\speciality{Génie des Télécommunications et Réseaux}
%\speciality{Génie Informatique des Systèmes Industriels}

%% Encadrant professionnel
\proFramerName{Monsieur Adel Amri}
\proFramerSpeciality{CTO}

%% Encadrant académique
\academicFramerName{Madame Sonia Gharsalli}
\academicFramerSpeciality{Maître-assistant}

%% Entreprise d'accueil
\companyName{DeepShift AI Academy}

%% Année universitaire
\collegeYear{2024 - 2025}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{J'autorise l'étudiant à faire le dépôt de son rapport de stage en vue d'une soutenance.}

\academicSignSentence{J'autorise l'étudiant à faire le dépôt de son rapport de stage en vue d'une soutenance.}

%%% FR
\frenchAbstract{

Face à la croissance rapide des besoins en automatisation et en intelligence opérationnelle, ce projet vise à développer un ensemble d’agents d’intelligence artificielle (IA) dédiés à des cas d’usage concrets en entreprise : veille concurrentielle, gestion automatique de backlog, vérification de conformité technique, et chatbot de support client.

Chaque agent repose sur un workflow d’automatisation intelligent, combinant modèles de langage (LLM), n8n, et diverses intégrations (Trello, Google Drive, Gmail, API internes). Le projet met l’accent sur la structuration des prompts, la validation des sorties JSON, et l’évaluation comparative de modèles d’IA (GPT-4o, Gemini).

Les résultats démontrent le potentiel des architectures multi-agents pour améliorer la productivité, fiabiliser les analyses, et réduire les erreurs humaines dans les processus métier.

}
\frenchAbstractKeywords{Intelligence artificielle, automatisation, agents autonomes, workflow, n8n, LLM, chatbot, entreprise intelligente.}

%%% EN
\englishAbstract{As organizations increasingly seek to enhance operational efficiency through intelligent automation, this project focuses on developing a set of AI agents implementing concrete enterprise use cases such as competitive intelligence, automated backlog generation, technical compliance verification, and a customer support chatbot.

Each agent is built upon an intelligent automation workflow that combines Large Language Models (LLMs) with n8n orchestration and integrations such as Trello, Google Drive, Gmail, and internal APIs. The project emphasizes prompt engineering, structured JSON output validation, and benchmarking of AI models (GPT-4o, Gemini).

The results highlight the potential of multi-agent architectures to boost productivity, enhance analytical reliability, and minimize human error across business processes.
}

\englishAbstractKeywords{Artificial Intelligence, automation, autonomous agents, workflow, n8n, LLM, chatbot, smart enterprise.}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{false}

\companyEmail{contact@company.com}
\companyTel{71 111 111}
\companyFax{71 222 222}
\companyAddressAR{نهج بحيرة ملاران - ضفاف البحيرة - تونس}
\companyAddressFR{Rue du Lac Malaren, Les Berges du Lac 1053 Tunis}